### 2019-02-26 report/final-report.tex
fixed Figure 1 text
drafted summary section

@@

    \node[text width=2.3cm,minimum height=.6cm,align=center,draw,rectangle] [right = 1.45cm of todnfregex.east] (synthdnflens) {\SynthDNFLens{}};
    \node[align=center] [above = .7cm of synthdnflens] (optician) {\Optician{}};

>>>>

Maintaining software systems that manage evolving representations of
data is tedious and error prone.  In this study, we have developed
algorithms for automatically synthesizing \emph{lenses}, which are
software adaptors that convert between two different representations
of the same information.  Lenses are a special form of program that
guarantee so-called \emph{round-tripping properties} that ensure the
transformations are well-behaved.  Our synthesis algorithms take as
input (i) the \emph{type} of each source as a regular expression, as
well as (ii) a small collection of representative \emph{examples} of
the desired translation.  They produceas output \emph{bijective string
  lenses}.  Bijective string lenses are a special class of lenses that
only exist when the two data sources are related via a bijection.
Despite this limitation, bijections and bijective synthesis form a
useful foundation on top of which more general transformations between
data sets may be built.  We explore two of these extensions: quotient
lenses and symmetric lenses.  Quotient lenses apply when two formats
are ``morally'' but not technically bijective.  Examples include two
formats that differ in their use of white space or in the order of
sequences of elements.  Symmetric lenses allow one side or the other to have
information not present in the other.  When converting between the
formats, defaults take the place of missing information.

We measured the effectiveness of our
algorithms on a set of 39 benchmarks drawn from Augeas~\cite{augeas},
which is a system for transforming and editing Linux configuration
files, and from FlashFill~\cite{flashfill}, which is an extension to
Microsoft Excel for synthesizing columns of spreadsheets.
On these benchmarks, we find it is possible to synthesize lenses of
comparable quality to hand-written lenses from format descriptions and
a very small number of examples, leveraging 
the large amount of information embedded in the format descriptions. 
We further found that as the formats diverge and the class of lenses
between them becomes richer, the synthesis problem becomes more
difficult and additional heuristics need to be considered.

We have written
papers~\cite{bijective-synthesis,quotient-synthesis,symmetric-synthesis}
describing and evaluating our algorithms. We produced open-source 
code~\cite{GitHub} that implements those algorithms.  In this report,
we summarize our key methods, results, and findings, focusing
on the core algorithms for bijective synthesis and quotient synthesis.

@@

    \node[text width=3.1cm,minimum height=.6cm,align=center,draw,rectangle] [right = 1.45cm of todnfregex.east] (synthdnflens) {\SynthDNFLens{}};
    \node[align=center] [above = .7cm of synthdnflens] (optician) {\Optician{}};
